---
title: "data_analysis_template"
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 2
    toc_float: true
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: monochrome
    theme: cerulean
    latex_engine: xelatex
---


# Scenario 

Type out a little bit about your experiment here

# Load packages 

```{r load-packages-1, warning=FALSE}

```


# Import data 

```{r import-data-1, message=FALSE}

```

# Data manipulation 

```{r data-manipulation-1, warning=FALSE}

```

# Exploratory data analysis {.tabset}

```{r}

```

# Descriptive statistics 
```{r descriptive-statistics}

```


# Fit model [random factors] 

```{r}

```

# Fit Models [Fixed factors]

```{r}

```

# Model Comparisons 

```{r}

```

# Model validation {.tabset}

## DHARMa residuals 
```{r model-validation-2}

```

## performance 

```{r}

```

# Model investigation {.tabset}

## summary 

```{r summary-100}

```

## ANOVA 

```{r Anova}

```

## R2 

```{r r-squared}

```

## emmeans - pariwise 

```{r emmeans-pairwise}

```

## probabilities 
```{r probabilities}

```
## {-}

# Summary figure 

```{r summary-figure-1}

```

