---
title: "data_analysis_template"
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 2
    toc_float: true
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: monochrome
    theme: cerulean
    latex_engine: xelatex
---


# Scenario 

Type out a little bit about your experiment here

# Load packages 

Careful what order you load your libraries in. The newest package loaded will have priority and can replace arguments that have the same names in other packages. 

```{r load-packages, warning=FALSE, message =FALSE}
library("tidyverse") # data manipulation and plotting
library("modelsummary") # descriptive statistics 
library("MuMIn") # model comparison
library("DHARMa") # model validation 
library("performance") # model validation 
library("car")
```


# Import data 

```{r import-data-1, message=FALSE}
data <- read.delim("data/example_data.txt")
```

# Data manipulation 

```{r data-manipulation-1, warning=FALSE}
data2 <- data |> 
  mutate(independent_var2 = independent_var+6)
```

# Exploratory data analysis {.tabset}

```{r warning =FALSE, message =FALSE}
ggplot(data2, aes(y=response_var, x=independent_var2, color =group)) + 
  geom_point() + 
  geom_smooth(method ="lm") + 
  theme_classic()
```

# Descriptive statistics 

A very useful package for descriptive statistics is a package called (model summary)[https://modelsummary.com/vignettes/datasummary.html]
```{r descriptive-statistics}
datasummary(response_var * group ~ Mean + Median + SD + N, data =data2)
```


# Fit model [random factors] 

```{r}

```

# Fit Models [Fixed factors]

```{r}
mod1 <- lm(response_var ~ independent_var * group, data = data2) 
mod2 <- lm(response_var ~ independent_var * group * independent_var2, data =data2)
```

# Model Comparisons 

```{r}
AICc(mod1, mod2, k=4)
```

# Model validation {.tabset}

## DHARMa residuals 
```{r model-validation-2}
simulateResiduals(mod1, plot=TRUE)
```

## performance 

```{r}
check_model(mod1)
```

# Model investigation {.tabset}

## summary 

```{r summary-100}
summary(mod1)
```

## ANOVA 

```{r Anova}
car::Anova(mod1)
```

## R2 

```{r r-squared}
r2(mod1)
```

## emmeans - pariwise 

```{r emmeans-pairwise}
mod1 |> emmeans(pairwise~group, type="response") |> summary()
```

## {-}

# Summary figure 

```{r summary-figure-1}
summary_figure <- ggplot(data2, aes(y=response_var, x=independent_var2, color =group)) + 
  geom_point() + 
  geom_smooth(method ="lm") + 
  theme_classic() 


pdf("outputs/summary_figure.pdf", width =6, height=4)
summary_figure
dev.off()
```

